Tulai

### 2023-09-06 Tulai-trash.qmd
test

```{r}
```

@@

Summary tables: 
1.AREA
```{r}
# Create a summary table
summary_table_area <- tl_final %>%
  group_by(area) %>%
  summarise(
    `Cores (n)` = sum(!is.na(core) & core != ""),
    `Core rejuvenations pieces (n)` = sum(!is.na(corefrag) & corefrag != ""),
    `Blade (n)` = sum(blank == "blade", na.rm = TRUE),
    `Flake (n)` = sum(blank == "flake", na.rm = TRUE),
    `Bladelet (n)` = sum(blank == "bladelet", na.rm = TRUE),
    `Retouched Tools (n)` = sum(retouch == 1, na.rm = TRUE),
    `Utilized (n)` = sum(utilization == 1, na.rm = TRUE),
    `Sickle Shine (n)` = sum(`sickle shine` == 1, na.rm = TRUE)
  )

@@

2.LAYER
```{r}
# Create a summary table
summary_table_layer <- tl_final %>%
  group_by(layer) %>%  # Note that 'area' is replaced with 'layer'
  summarise(
    `Cores (n)` = sum(!is.na(core)),  # Count non-NA core entries
    `Core rejuvenations pieces (n)` = sum(!is.na(corefrag)),  # Count non-NA corefrag entries
    `Blade (n)` = sum(blank == "blade", na.rm = TRUE),
    `Flake (n)` = sum(blank == "flake", na.rm = TRUE),
    `Bladelet (n)` = sum(blank == "bladelet", na.rm = TRUE),
    `Retouched Tools (n)` = sum(retouch == 1, na.rm = TRUE),
    `Utilized (n)` = sum(utilization == 1, na.rm = TRUE),
    `Sickle Shine (n)` = sum(`sickle shine` == 1, na.rm = TRUE)
  )

@@

AREA_LAYER:
```{r}
# Create a summary table based on the 'al' column
summary_table_al <- tl_final %>%
  group_by(al) %>%  
  summarise(
    `Cores (n)` = sum(!is.na(core)),  # Count non-NA core entries
    `Core rejuvenations pieces (n)` = sum(!is.na(corefrag)),  # Count non-NA corefrag entries
    `Blade (n)` = sum(blank == "blade", na.rm = TRUE),
    `Flake (n)` = sum(blank == "flake", na.rm = TRUE),
    `Bladelet (n)` = sum(blank == "bladelet", na.rm = TRUE),
    `Retouched Tools (n)` = sum(retouch == 1, na.rm = TRUE),
    `Utilized (n)` = sum(utilization == 1, na.rm = TRUE),
    `Sickle Shine (n)` = sum(`sickle shine` == 1, na.rm = TRUE)
  )

@@

# Adding a new row with total counts
# Adding a new row with total counts
summary_table_area <- summary_table_area %>% 
  add_row(
    area = "Total",
    blade_count = sum(summary_table_area$blade_count, na.rm = TRUE),
    flake_count = sum(summary_table_area$flake_count, na.rm = TRUE),
    bladelet_count = sum(summary_table_area$bladelet_count, na.rm = TRUE),
    tool_count = sum(summary_table_area$tool_count, na.rm = TRUE),
    core_count = sum(summary_table_area$core_count, na.rm = TRUE),
    core_rejuvenation_count = sum(summary_table_area$core_rejuvenation_count, na.rm = TRUE),
    retouched_tool_count = sum(summary_table_area$retouched_tool_count, na.rm = TRUE),
    utilized_tool_count = sum(summary_table_area$utilized_tool_count, na.rm = TRUE),
    shine_tool_count = sum(summary_table_area$shine_tool_count, na.rm = TRUE),
    total = sum(summary_table_area$total, na.rm = TRUE)  # Explicitly setting the total
  )

@@

                        UniqueDO NOT RUN

@@

consistency in dimention:
```{r}
#|label: fig_2
#|fig-cap: "Boxplot for each Dimention"
#|fig-height: 5

@@

```{r}
# Load necessary libraries
# Import required packages
library(ggplot2)
library(ggpmisc)

# Create the data frame based on the example table
summary_table2_area <- data.frame(
  area = c("D1_a", "D1_c", "TA_d", "TA_e", "TP1_c"),
  lithic_volumetric_density = c(51.43, 111.11, 45.13, 100.08, 212.50),
  retouch_frequency = c(0.05, 0.09, 0.07, 0.07, 0.10)
)

# Generate the regression plot
p <- ggplot(summary_table2_area, aes(x = lithic_volumetric_density, y = retouch_frequency)) +

  # Titles and labels
  labs(title = "Relationship between Retouch Frequency and Lithic Volumetric Density",
       x = "Lithic Volumetric Density",
       y = "Retouch Frequency")

@@

@@

WABI: 
```{r}
# regression plot-layer
library(ggplot2)
library(ggpmisc)

>>>>

@@

Summary tables: 1.AREA

```{r}
# Create a summary table
summary_table_area <- tl_final %>%
  group_by(area) %>%
  summarise(
    `Cores (n)` = sum(!is.na(core) & core != ""),
    `Core rejuvenations pieces (n)` = sum(!is.na(corefrag) & corefrag != ""),
    `Blade (n)` = sum(blank == "blade", na.rm = TRUE),
    `Flake (n)` = sum(blank == "flake", na.rm = TRUE),
    `Bladelet (n)` = sum(blank == "bladelet", na.rm = TRUE),
    `Retouched Tools (n)` = sum(retouch == 1, na.rm = TRUE),
    `Utilized (n)` = sum(utilization == 1, na.rm = TRUE),
    `Sickle Shine (n)` = sum(`sickle shine` == 1, na.rm = TRUE)
  )

@@

2.LAYER

```{r}
# Create a summary table
summary_table_layer <- tl_final %>%
  group_by(layer) %>%  # Note that 'area' is replaced with 'layer'
  summarise(
    `Cores (n)` = sum(!is.na(core)),  # Count non-NA core entries
    `Core rejuvenations pieces (n)` = sum(!is.na(corefrag)),  # Count non-NA corefrag entries
    `Blade (n)` = sum(blank == "blade", na.rm = TRUE),
    `Flake (n)` = sum(blank == "flake", na.rm = TRUE),
    `Bladelet (n)` = sum(blank == "bladelet", na.rm = TRUE),
    `Retouched Tools (n)` = sum(retouch == 1, na.rm = TRUE),
    `Utilized (n)` = sum(utilization == 1, na.rm = TRUE),
    `Sickle Shine (n)` = sum(`sickle shine` == 1, na.rm = TRUE)
  )

@@

AREA_LAYER:

```{r}
# Create a summary table based on the 'al' column
summary_table_al <- tl_final %>%
  group_by(al) %>%  
  summarise(
    `Cores (n)` = sum(!is.na(core)),  # Count non-NA core entries
    `Core rejuvenations pieces (n)` = sum(!is.na(corefrag)),  # Count non-NA corefrag entries
    `Blade (n)` = sum(blank == "blade", na.rm = TRUE),
    `Flake (n)` = sum(blank == "flake", na.rm = TRUE),
    `Bladelet (n)` = sum(blank == "bladelet", na.rm = TRUE),
    `Retouched Tools (n)` = sum(retouch == 1, na.rm = TRUE),
    `Utilized (n)` = sum(utilization == 1, na.rm = TRUE),
    `Sickle Shine (n)` = sum(`sickle shine` == 1, na.rm = TRUE)
  )

@@

# Adding a new row with total counts
summary_table_area <- summary_table_area %>% 
  add_row(
    area = "Total",
    blade_count = sum(summary_table_area$blade_count, na.rm = TRUE),
    flake_count = sum(summary_table_area$flake_count, na.rm = TRUE),
    bladelet_count = sum(summary_table_area$bladelet_count, na.rm = TRUE),
    tool_count = sum(summary_table_area$tool_count, na.rm = TRUE),
    core_count = sum(summary_table_area$core_count, na.rm = TRUE),
    core_rejuvenation_count = sum(summary_table_area$core_rejuvenation_count, na.rm = TRUE),
    retouched_tool_count = sum(summary_table_area$retouched_tool_count, na.rm = TRUE),
    utilized_tool_count = sum(summary_table_area$utilized_tool_count, na.rm = TRUE),
    shine_tool_count = sum(summary_table_area$shine_tool_count, na.rm = TRUE),
    total = sum(summary_table_area$total, na.rm = TRUE)  # Explicitly setting the total
  )

@@

                      #########DO NOT RUN0

@@

consistency in dimention:

```{r}
#|label: fig_2
#|fig-cap: "Boxplot for each Dimention"
#|fig-height: 5

@@

```{r}
# Load necessary libraries
library(tidyverse)
library(ggpmisc)

# Create the data frame
summary_table2_area <- tibble(
  area = c("D1_a", "D1_c", "TA_d", "TA_e", "TP1_c"),
  lithic_volumetric_density = c(51.43, 111.11, 45.13, 100.08, 212.50),
  retouch_frequency = c(0.05, 0.09, 0.07, 0.07, 0.10)
)

# Create the ggplot
p <- ggplot(summary_table2_area, 
            aes(x = lithic_volumetric_density,
                                     y = retouch_frequency)) +

  # Add points
  geom_point(color = 
               "black", 
             size = 2) +

  # line with log scale
  stat_smooth(method = "lm", 
              formula = y ~ log(x), 
              se = TRUE, aes(group = 1), 
              color = "blue", 
              size = 0.5) +

  # Add text labels for each point
  geom_text(aes(label = area), 
            vjust = -1, 
            hjust = -0.5, 
            size = 2.5) +

  # Add regression equation, R-squared, and p-value
  stat_poly_eq(aes(label = paste(stat(eq.label), stat(rr.label), stat(p.value.label), sep = "~~~")),
               formula = y ~ log(x), 
               parse = TRUE, 
               size = 2) +

  # Add titles and labels
  labs(
    title = "Relationship between Retouch Frequency and Lithic Volumetric Density",
    x = "Lithic Volumetric Density",
    y = "Retouch Frequency"
  ) +

  scale_x_log10() +

  theme(
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 10),
    plot.title = element_text(size = 12)
  )

@@

library(googlesheets4)

data_sheet <- "https://docs.google.com/spreadsheets/d/16yLb-RyIQ7x2jFEH_Q7OZYTwlEAXJgFu/edit#gid=2014421097"

sum_depth_sheet <- read_sheet(data_sheet, sheet = "sum_depth")

@@

WABI:

```{r}
# regression plot-layer
library(ggplot2)
library(ggpmisc)
